### 2017-09-26 TF-vldb2018/sec-dynamicTopk.tex

Intuitively, we want (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
Thus we define the {\em pattern fragmentation} problem. Given $P$ and a positive integer $h$, it is to find
an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized.
\revise{The bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
	while minimizing the cut size between pattern fragments.}

>>>>

\vspace{0.8ex}
Intuitively, we want (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
Thus we define the {\em pattern fragmentation} problem. Given $P$ and a positive integer $h$, it is to find
an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized.
\revise{The bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
	while minimizing the cut size between pattern fragments.}
